\documentclass{article}

% Shrink margins
\usepackage[margin=.9in]{geometry}

% For hyperlinks
\usepackage{hyperref}

% For making compact lists with itemize* environment
\usepackage{mdwlist}

% Fancy sections
\newcommand{\ressection}[1]{\noindent{\large\textbf{#1}}\vspace{2pt}\hrule\vspace{4pt}}

% For items with dates: \hfill fills up horizontal space until the
% words to the left and the right are as far apart as possible
\newcommand{\leftandright}[2]{\noindent\textbf{#1}\hfill\textbf{#2}}

\newcommand{\leftandrighti}[2]{\indent\textit{#1}\hfill\textit{#2}}

% Remove page numbering
\pagestyle{empty}

\begin{document}

%% Change font family
\sffamily

\begin{center}
\textbf{\huge{Steven~P.~Wright}}

\href{mailto:sprw121@gmail.com}{sprw121@gmail.com}
\textbullet\, 415 233 3077
\textbullet\, \href{https://github.com/sprw121}{http://github.com/sprw121}
\end{center}

\ressection{Work experience}

\leftandright{Uber, UberWorks}{Chicago, IL and San Francisco, CA} \\
\leftandrighti{Senior Data Scientist}
	      {January 2018 - June 2020}
\begin{itemize*}
\item Cofounding member of UberWorks, a new line of business in the temporary labor space. Grew from a successful incubator project into a wholely owned subsiduary. Scaled past a 10MM run rate with positive operating margins. Held several roles throughout the course of the project.
\item As the first engineer on the team, I personally built the majority of the backend API server and data infrastructure for the V0 and V1 products.
\item As the team grew and specialized, I became responsible for our matching and dispatch systems, both from a technical and product perspective. Designed the end to end system, including operational processes, product experiences and technical architecture involved in finding the best matches to reliably fill shifts.
\item Designed the core data models behind the order management, onboarding, matching, and dispatch systems.
\item Architected several major integrations with third party vendors to deliver instant dispersements of payments to our workers upon completion of a shift.
\item Determined and tracked the KPIs that best measured and shaped behavior toward our business goals.
\item Determined strategies for both worker and business side pricing, and set rates.
\end{itemize*}

\leftandright{Uber, Marketplace Optimization Advanced Development}{San Francisco, CA} \\
\leftandrighti{Data Scientist II}
	      {January 2017 - December 2017}
\begin{itemize*}
\item Core contributor to Uber's core structural pricing algorithm. Helped develop a network flow model of Uber's personal transport products. Our model had several major impacts on Uber's pricing systems; moving from an origin only pricing system to origin-destination aware, calculated marginal supply hour values, and incorporating cross product elasticity. Resulted in a 2\% increase in both trips and operating profit.
\item Introduced a set of python wrappers around Vowpal Wabbit to allow data scientists to easily develop small to medium size (up to 100M rows, 10M's of parameters) sparse regression models on Uber data sources quickly and with minimal overhead going to production. Used across multiple teams and projects.
\end{itemize*}

\leftandright{AdRoll}{San Francisco, CA} \\
\leftandrighti{Senior Data Scientist}
	      {January 2016 - August 2016}\\
\leftandrighti{Data Scientist}
	      {December 2014 - January 2016}

\begin{itemize*}
\item Senior engineer for AdRoll's real time bid pricing algorithms, utilizing
  large scale machine learning to predict user actions and price impressions accordingly.
  Priced \textgreater \$150 million in ad spend per year.
\item Architected and implemented AdRoll's real-time data pipeline to provide up to date
  user browsing data at bid time. (http://tech.adroll.com/blog/data-science/2015/12/08/data-science\_event\_processing.html)
\item Designed algorithms to adjust bid prices to exploit auction dynamics across
  different ad exchanges.
\item Responsible for the latency sensitive real-time bid pricing server,
  maintained \textless .01\% timeout rate at a 1ms SLA.
\item Core contributor to the in house supervised learning system. Designed the
  data IO and caching subsystem, contributed to feature engineering and learning frameworks,
  parallelization, vectorization and debugging of learning algorithms: SDCA, LBFGS, AGAGRAD,
  Factorization Machines.
\end{itemize*}

\leftandright{Spire Global, Inc}{San Francisco, CA} \\
\leftandrighti{Software Engineer}{May - October 2014}

\begin{itemize*}
\item Implemented an on board satellite telemetry data logging and analysis system.
\item Contributed to the development of Raptor data encoding for data transfer over
  UDP connections with high packet loss rates.
\item Developed application layer command-and-control protocol for satellite components.
\end{itemize*}

\leftandright{Deep Blue Capital Management}{San Francisco, CA} \\
\leftandrighti{Intern}{January - June 2013}\\

\leftandright{UCSF, Biostatistics}{San Francisco, CA} \\
\leftandrighti{Intern}{May - September 2012}\\

\ressection{Education}

\leftandright{University of California, Santa Barbara, \textmd{B.S. Applied
    Mathematics and Statistics}}{2009 - 2013}
\begin{itemize*}
\item \textbf{Relevant coursework:} Statistical Theory, Graduate Time Series,
  Graduate Multivariate Statistics, Graduate Financial Mathematics,
  Numerical Analysis, Partial Differential Equations,
  Advanced Linear Algebra, Stochastic Processes, Real Analysis,
  Microeconomics, Fixed Income Markets, Data Structures, Algorithms.
\item Designed and implemented a low latency limit order matching engine,
  competitive with top entrants to QuantCup.
  (https://github.com/sprw121/matching\textunderscore engine)
\end{itemize*}

\vspace{1.0em}

\ressection{Skills}

\begin{itemize*}
\item \textbf{Profession Experience:} C, D, Python, Erlang, AWS, GCP, Linux, Node, React.
\item Extensive work in the area of marketplace design, pricing and matching systems.
\item Experience building scalable, high performance machine learning systems,
  real time data systems, low latency server design, and engineering in
  constrained resource environments.
\item Proven ability to provide technical leadership, project management,
  and coordinate development with multiple teams.
\end{itemize*}

\end{document}
